Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-03 wearables_survey.tex
Added keywords, wrote 1/3 related work sections.

% A category with the (minimum) three required fields
\category{look it up}{keyword1}{keyword2}{keyword3}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{term1} {term2} {term3}

@@

\section{Related Work}
In this section, we discuss related work which explores threats for smartphones and wearable devices, discusses emerging challenges related to ubiquitous computing, and studies user perceptions of threats and technologies.

@@

\subsection{Ubiquitous Computing}
(REDO) As technology becomes more and more ubiquitous, more sensors will record more things about more people more of the time. There are an endless amount of unique situations which can negatively impact a person's privacy or security. There is a clear need to better communicate these risks to people (cite webcam paper and other papers here?), but there are too many things to warn people about. Therefore, we need to know what are the most threatening and also most relevant situations to inform the users about, since we can't bug them all the time about everything.

We need to investigate the threat landscape and people's privacy concerns now, before wearables are widely adopted, or designed without these considerations in mind. So although our research is at at time when things are rapidly changing and most people don't have wearables, it is crucial to do the research now so we can prevent badness later.

>>>>

% A category with the (minimum) three required fields
\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

\terms{Human Factors}{Measurement}{Security}

@@

\section{Related Work}
In this section, we discuss related work which discusses emerging challenges related to ubiquitous computing, explores threats for smartphones, and studies user perceptions of threats and technologies.

\subsection{Ubiquitous Sensing}
Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}. More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}. The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}. Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.

@@

We are the first study of this kind! Wheee, say it explicitly.
